---
title: "Results"
date: '2022-06-21'
---

# set up environement 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)

### Load packages
library(dplyr)
library(sp)
library(ggplot2)
library(rgdal)
library(INLA)
library(inlabru)
library(RColorBrewer)
library(rgeos)
library(raster)
library(egg)
library(sf)
library(usdm)
library(ggspatial)
library(rasterVis)

# Specify experimental BRU options 
bru_options_set(inla.mode = "experimental")

# Load the data and models 
load("trapping_data.Rda")
load("optimal_mod.Rda")
load("mod_4_older_fit.Rda")
load("mod_4_younger_fit.Rda")
load("mesh.Rda")

# Create the individual objects 
Boundary <- trapping_data$Boundary
Trap_Hunt_spatial <- trapping_data$Trap_Hunt_spatial
landcover <- trapping_data$landcover
valley_ridge_dis <- trapping_data$valley_ridge_dis
Road_dis <- trapping_data$Road_dis
travel_time <- trapping_data$travel_time
Sources <- trapping_data$Sources
```


# Methods #

### Plot of spatial variables ###

```{r}
### Plot spatial variables - Figure 1 
# Boundary, mesh, traps, and source points 
P1 <- ggplot() +
  gg(trapping_data$Boundary)+
  gg(trapping_data$Trap_Hunt_spatial, color = "black", cex = 0.01) +
  gg(trapping_data$Sources, color = "blue", cex = 1) +
  coord_equal(xlim = c(183.2336, 197.6343), ylim = c(9849.702, 9867.437)) +
  theme(axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        axis.text.x=element_blank(),
        axis.text.y=element_blank()) +
  annotation_scale(plot_unit = "km") +
  annotation_north_arrow(style = north_arrow_minimal, pad_y = unit(1, "cm"), pad_x = unit(-0.5, "cm"))

# Land cover
P2 <- ggplot() +
  gg(trapping_data$Boundary)+
  gg(trapping_data$landcover)+
  coord_equal(xlim = c(183.2336, 197.6343), ylim = c(9849.702, 9867.437)) +
  theme(axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        axis.text.x=element_blank(), 
        axis.text.y=element_blank()) + 
  guides(fill=guide_legend(title="Dense forest\ndistance\n(100m)"))

# Distance to ridgeline or valley bottoms
P3 <- ggplot() +
  gg(trapping_data$Boundary)+
  gg(trapping_data$valley_ridge_dis)+
  coord_equal(xlim = c(183.2336, 197.6343), ylim = c(9849.702, 9867.437)) +
  theme(axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        axis.text.x=element_blank(), 
        axis.text.y=element_blank()) + 
  guides(fill=guide_legend(title="Ridge/valley\ndistance\n(100m)"))

# Distance to road
P4 <- ggplot() +
  gg(trapping_data$Boundary)+
  gg(trapping_data$Road_dis)+
  coord_equal(xlim = c(183.2336, 197.6343), ylim = c(9849.702, 9867.437)) +
  theme(axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        axis.text.x=element_blank(),
        axis.text.y=element_blank())+ 
  guides(fill=guide_legend(title="Road distance\n(1km)"))

# Travel time 
P5 <- ggplot() +
  gg(trapping_data$Boundary)+
  gg(trapping_data$travel_time)+
  coord_equal(xlim = c(183.2336, 197.6343), ylim = c(9849.702, 9867.437)) +
  theme(axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        axis.text.x=element_blank(),
        axis.text.y=element_blank())+ 
  guides(fill=guide_legend(title="Travel time\n(hours)"))

# Save plot - jpeg
ggsave(
  "Figure_1.jpeg",
  plot = egg::ggarrange(P1, P2, P3, P4, P5,  ncol = 2, labels = c("a.", "b.", "c.", "d.", "e.")),
  width = 184 ,
  height =  220,
  units = c("mm"),
  dpi = 800
)

# Save plot - eps
ggsave(
  "Figure_1.eps",
  plot = egg::ggarrange(P1, P2, P3, P4, P5,  ncol = 2, labels = c("a.", "b.", "c.", "d.", "e.")), 
  width = 184,
  height = 220,
  units = c("mm"),
  dpi = 800
)

### Plot the mesh - Figure S1
P1_SI <- ggplot() +
  gg(mesh) +
  gg(trapping_data$Boundary)+
  gg(trapping_data$Trap_Hunt_spatial, color = "black", cex = 0.01) +
  gg(trapping_data$Sources, color = "blue", cex = 1) +
  coord_equal(xlim = c(177.1975, 205.1002), ylim = c(9845.0620, 9872.7841)) +
  theme(axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        axis.text.x=element_blank(),
        axis.text.y=element_blank()) +
  annotation_scale(plot_unit = "km") +
  annotation_north_arrow(style = north_arrow_minimal, pad_y = unit(1, "cm"), pad_x = unit(-0.5, "cm"))

# Save plot - jpeg
ggsave(
  "Figure_S1.jpeg",
  plot = P1_SI,
  width = 500,
  height = 500,
  units = c("mm"),
  dpi = 800
)

# Save plot - eps
ggsave(
  "Figure_S1.eps",
  plot = P1_SI, 
  width = 500,
  height = 500,
  units = c("mm"),
  dpi = 800
)
```

### Respondents ###

```{r}
### Respondent descriptive statistics
# Subset to year
Phase_2005 <- subset(Trap_Hunt_spatial, 2005==Trap_Hunt_spatial$Phase)
Phase_2010 <- subset(Trap_Hunt_spatial, 2010==Trap_Hunt_spatial$Phase)

# Trap numbers
trap_num_total <- length(unique(trapping_data$Trap_Hunt_spatial$Trap_ID))
trap_num_2005 <- length(unique(Phase_2005$Trap_ID))
trap_num_2010 <- length(unique(Phase_2010$Trap_ID))

# Hunter numbers
hunter_num_total <- length(unique(trapping_data$Trap_Hunt_spatial$Huntrnm))
hunter_num_2005 <- length(unique(Phase_2005$Huntrnm))
hunter_num_2010 <- length(unique(Phase_2010$Huntrnm))

# Trap type  
table(trapping_data$Trap_Hunt_spatial$Traptyp)

# Barrage or single
table(trapping_data$Trap_Hunt_spatial$Brrgors)

### Subset to hunters
Trap_Hunt_data <- data.frame(Trap_Hunt_spatial)
Trap_data_hunter <- Trap_Hunt_data %>% 
  group_by(Huntrnm) %>%
    filter(row_number()==1)

# Age
age_mean <- round(mean(Trap_data_hunter$Age),1)
age_sd <- round(sd(Trap_data_hunter$Age),1)

```

We counted `r trap_num_total` traps (`r trap_num_2005` in 2005 and `r trap_num_2010` in 2010) set by `r hunter_num_total` hunters (`r hunter_num_2005` from 2005 and `r hunter_num_2010` from 2010). Of these traps, `r table(trapping_data$Trap_Hunt_spatial$Traptyp)[1]` were 'toule', `r table(trapping_data$Trap_Hunt_spatial$Traptyp)[2]` were 'tsonde', and the remaining `r table(trapping_data$Trap_Hunt_spatial$Traptyp)[3]` were unknown or other trap types. Additionally, `r  table(trapping_data$Trap_Hunt_spatial$Brrgors)[2]` were set up as single traps and `r  table(trapping_data$Trap_Hunt_spatial$Brrgors)[1]` as 'barrage' traps (with the remaining `r  table(trapping_data$Trap_Hunt_spatial$Brrgors)[3]` classified as unknown or other). The hunters included in the sample had a mean age of `r age_mean` (standard deviation (SD) = `r age_sd`). Furthermore, `r table(Trap_data_hunter$Educatn)[1]` had primary-level education, `r table(Trap_data_hunter$Educatn)[2]` had secondary-level, and the remainder were unknown. 

### Statistical results ###

```{r}
# Posterior of each fixed effect
P1 <- plot(optimal_mod, rownames(optimal_mod$summary.fixed)[1]) +
  xlab("Distance to dense forest (100m)") +
  ylab("PDF")
  
P2 <- plot(optimal_mod, rownames(optimal_mod$summary.fixed)[2]) +
  xlab("Ridge/valley distance (100m)") +
  ylab("PDF")
  
P3 <- plot(optimal_mod, rownames(optimal_mod$summary.fixed)[3]) +
  xlab("Travel time (hours)") +
  ylab("PDF")
  
P4 <- plot(optimal_mod, rownames(optimal_mod$summary.fixed)[4]) +
  xlab("Intercept") +
  ylab("PDF")

# SPDE range and variance 
spde.range <- spde.posterior(optimal_mod, "mySmooth", what = "range")
spde.logvar <- spde.posterior(optimal_mod, "mySmooth", what = "log.variance")
P5 <- plot(spde.range) + xlab("SPDE range") + ylab("PDF")
P6 <- plot(spde.logvar) + xlab("SPDE log variance") + ylab("PDF")

# Save plot - jpeg
ggsave(
  "Figure_2.jpeg",
  plot = egg::ggarrange(P1, P2, P3, P4, P5, P6,   ncol = 2, labels = c("a.", "b.", "c.", "d.", "e.", "f.")),
  width = 184 ,
  height =  220,
  units = c("mm"),
  dpi = 800
)

# Save plot - eps
ggsave(
  "Figure_2.eps",
  plot = egg::ggarrange(P1, P2, P3, P4, P5, P6,  ncol = 2, labels = c("a.", "b.", "c.", "d.", "e.","f.")), 
  width = 184,
  height = 220,
  units = c("mm"),
  dpi = 800
)
```


```{r}
###### Summarise the main model results ######
### Plot the predicted density
# Create a empty object from the mesh
predict_df <- pixels(mesh, mask = Boundary, nx = 913 , ny = 913 )

# Make predictions from the model
int_1 <- predict(optimal_mod, predict_df, ~ list(
  all_pred = (dense_dis + layer + vall_rid_dis +  mySmooth + Intercept),
  dense_dis_pred = (dense_dis),
  layer_pred = (layer),
  vall_rid_dis_pred = (vall_rid_dis),
  smooth_pred = (mySmooth),
  Intercept_pred = (Intercept)
))

### save as tiff files 
# All variables
all_variables <- raster(int_1$all_pred) ; writeRaster(all_variables, filename = paste0("predicted/all_variables.tif"),options=c('TFW=YES'),  overwrite=TRUE)

# Distance to dense forest
dense_forest <- raster(int_1$dense_dis_pred) ; writeRaster(dense_forest, filename = paste0("predicted/dense_forest.tif"),options=c('TFW=YES'),  overwrite=TRUE)

# Travel time
travel_time <- raster(int_1$layer_pred) ; writeRaster(travel_time, filename = paste0("predicted/travel_time.tif"),options=c('TFW=YES'),  overwrite=TRUE)

# vallley distance 
valley_dis <- raster(int_1$vall_rid_dis_pred) ; writeRaster(valley_dis, filename = paste0("predicted/valley_dis.tif"),options=c('TFW=YES'),  overwrite=TRUE)

# SPDE
SPDE_var <- raster(int_1$smooth_pred) ; writeRaster(SPDE_var, filename = paste0("predicted/SPDE_var.tif"),options=c('TFW=YES'),  overwrite=TRUE)

# Summary
quantile(int_1$all_pred$mean) # all values below -27.306317 are in the bottom quantile 
# In arcmap, using the following in the raster calculator = Con("all_variables.tif"  <= -27.306317, 1 ,0)
# Clip the raster by the boundary area.

# Create binary variable showing areas below the 2nd quantile
all_variables_bin <- reclassify(all_variables, cbind(quantile(int_1$all_pred$mean)[2], Inf, 0), right=FALSE)
all_variables_bin <- reclassify(all_variables_bin, cbind(-Inf, quantile(int_1$all_pred$mean)[2], 1), right=FALSE)

# As factor
all_variables_bin_df <- as.data.frame(all_variables_bin, xy = TRUE) %>%
  mutate(mean = factor(mean))

# Save
writeRaster(all_variables_bin, filename = paste0("predicted/all_variables_bin.tif"),options=c('TFW=YES'),  overwrite=TRUE)

# Source points - communities and hunting camps
Refu_ex <- readOGR("predicted/Refu_ex.shp")
### Change map units from m to km 
Refu_ex <- spTransform(Refu_ex,"+proj=utm +zone=33 +south +datum=WGS84 +units=km +no_defs")
```

```{r}
# Plot the predicted hunting intensity
P1 <- ggplot() +
  gg(int_1$all_pred)+
  coord_equal(xlim = c(183.2336, 197.6343), ylim = c(9849.702, 9867.437)) +
  theme(axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        axis.text.x=element_blank(),
        axis.text.y=element_blank()) +
  ggtitle("All variables")

P2 <- ggplot() +
  gg(int_1$dense_dis_pred)+
  coord_equal(xlim = c(183.2336, 197.6343), ylim = c(9849.702, 9867.437)) +
  theme(axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        axis.text.x=element_blank(),
        axis.text.y=element_blank()) +
  ggtitle("Distance to dense forest (100m)")

P3 <- ggplot() +
  gg(int_1$layer_pred)+
  coord_equal(xlim = c(183.2336, 197.6343), ylim = c(9849.702, 9867.437)) +
  theme(axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        axis.text.x=element_blank(),
        axis.text.y=element_blank())  +
  ggtitle("Travel time (hours)")

P4 <- ggplot() +
  gg(int_1$vall_rid_dis_pred)+
  coord_equal(xlim = c(183.2336, 197.6343), ylim = c(9849.702, 9867.437)) +
  theme(axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        axis.text.x=element_blank(),
        axis.text.y=element_blank()) +
  ggtitle("Distance to valleys and ridges (100m)")

P5 <- ggplot() +
  gg(int_1$smooth_pred)+
  coord_equal(xlim = c(183.2336, 197.6343), ylim = c(9849.702, 9867.437)) +
  theme(axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        axis.text.x=element_blank(),
        axis.text.y=element_blank())+
  ggtitle("SPDE")

P6 <- ggplot() + 
  geom_raster(data = all_variables_bin_df, aes(x = x, y = y, fill = mean)) +
  scale_fill_manual(values = viridis::viridis(2), breaks = 0:1,
                    labels = c("Above", "Bottom")) + coord_equal(xlim = c(183.2336, 197.6343), ylim = c(9849.702, 9867.437)) +
  gg(Refu_ex, "grey")+
  theme(axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        axis.text.x=element_blank(),
        axis.text.y=element_blank()) + 
  guides(fill=guide_legend(title="Quantile")) 


# Save plot - jpeg
ggsave(
  "Figure_3.jpeg",
  plot = egg::ggarrange(P1, P2, P3, P4, P5, P6,  ncol = 2, labels = c("a.", "b.", "c.", "d.", "e.", "f.")),
  width = 184 ,
  height =  220,
  units = c("mm"),
  dpi = 800
)

# Save plot - eps
ggsave(
  "Figure_3.eps",
  plot = egg::ggarrange(P1, P2, P3, P4, P5, P6, ncol = 2, labels = c("a.", "b.", "c.", "d.", "e.", "f.")), 
  width = 184,
  height = 220,
  units = c("mm"),
  dpi = 800
)
```



```{r}
### Look at the posterior of the SPDE
corplot <- plot(spde.posterior(optimal_mod, "mySmooth", what = "matern.correlation"))
covplot <- plot(spde.posterior(optimal_mod, "mySmooth", what = "matern.covariance"))
egg::ggarrange(corplot, covplot,  ncol = 2, labels = c("a.", "b."))

# Save plot - jpeg
ggsave(
  "Figure_S2.jpeg",
  plot = egg::ggarrange(corplot, covplot,  ncol = 1, labels = c("a.", "b.")),
  width = 100 ,
  height =  120,
  units = c("mm"),
  dpi = 800
)

# Save plot - eps
ggsave(
  "Figure_S2.eps",
  plot = egg::ggarrange(corplot, covplot,  ncol = 1, labels = c("a.", "b.")), 
  width = 100,
  height = 120,
  units = c("mm"),
  dpi = 800
)

```

### Age model 


```{r}
# Subset to hunters
Trap_Hunt_data <- data.frame(Trap_Hunt_spatial)
Trap_Hunt_data <- Trap_Hunt_data_df %>% 
  group_by(Huntrnm) %>%
  filter(row_number()==1)

# mean age 
age_mean <- mean(Trap_Hunt_data$Age)

# Split the sample into younger and older respondents, based on the median
Trap_Hunt_spatial_older <- Trap_Hunt_spatial[Trap_Hunt_spatial$Age > age_mean ,]
Trap_Hunt_spatial_younger <- Trap_Hunt_spatial[Trap_Hunt_spatial$Age <= age_mean,]

old_traps <- nrow(Trap_Hunt_spatial_older)
young_traps <- nrow(Trap_Hunt_spatial_younger)
prop_old <- paste0(round( (nrow(Trap_Hunt_spatial_older)/nrow(Trap_Hunt_spatial))*100, 1),"%")
```

In total, `r old_traps` (`r prop_old`) of the traps were set by hunters in the ‘more experienced’ sub-group, with the remaining `r young_traps` traps set by those in the ‘less experienced’ group. 

```{r}
### Posterior of each fixed effect
# Forest
P1.a <- plot(mod_4_older_fit, rownames(mod_4_older_fit$summary.fixed)[1]) +
  xlab("Distance to dense forest (100m)") +
  ylab("PDF") + geom_area(fill = '#b3e2cd', alpha=0.2) 
  
P1.b <- plot(mod_4_younger_fit, rownames(mod_4_younger_fit$summary.fixed)[1]) +
  xlab("Distance to dense forest (100m)") +
  ylab("PDF") + geom_area(fill = '#fdcdac', alpha=0.2)

# Valley
P2.a <- plot(mod_4_older_fit, rownames(mod_4_older_fit$summary.fixed)[2]) +
  xlab("Ridge/valley distance (100m)") +
  ylab("PDF") + geom_area(fill = '#b3e2cd', alpha=0.2) 
  
P2.b <- plot(mod_4_younger_fit, rownames(mod_4_younger_fit$summary.fixed)[2]) +
  xlab("Ridge/valley distance (100m)") +
  ylab("PDF") + geom_area(fill = '#fdcdac', alpha=0.2) 

# Travel
P3.a <- plot(mod_4_older_fit, rownames(mod_4_older_fit$summary.fixed)[3]) +
  xlab("Travel time (hours)") +
  ylab("PDF")  + geom_area(fill = '#b3e2cd', alpha=0.2) 
  
P3.b <- plot(mod_4_younger_fit, rownames(mod_4_younger_fit$summary.fixed)[3]) +
  xlab("Travel time (hours)") +
  ylab("PDF")  + geom_area(fill = '#fdcdac', alpha=0.2) 

# Intercept
P4.a <- plot(mod_4_older_fit, rownames(mod_4_older_fit$summary.fixed)[4]) +
  xlab("Intercept") +
  ylab("PDF") + geom_area(fill = '#b3e2cd', alpha=0.2) 

P4.b <- plot(mod_4_younger_fit, rownames(mod_4_younger_fit$summary.fixed)[4]) +
  xlab("Intercept") +
  ylab("PDF") + geom_area(fill = '#fdcdac', alpha=0.2) 


# Save plot - jpeg
ggsave(
  "Figure_4.jpeg",
  plot = egg::ggarrange(P1.a, P1.b, P2.a, P2.b, P3.a, P3.b, P4.a , P4.b ,  ncol = 2, labels = c("a.", "b.", "c.", "d.", "e.", "f.", "g.", "h.")),
  width = 184 ,
  height =  240,
  units = c("mm"),
  dpi = 800
)

# Save plot - eps
ggsave(
  "Figure_4.eps",
  plot = egg::ggarrange(P1.a, P1.b, P2.a, P2.b, P3.a, P3.b, P4.a , P4.b ,  ncol = 2, labels = c("a.", "b.", "c.", "d.", "e.", "f.", "g.", "h.")), 
  width = 184,
  height = 240,
  units = c("mm"),
  dpi = 800
)
```



